Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-04-01 paper.tex
reformatted schedules 09-0*
new 08-06 schedules with critique

\section{Sample Schedules}\label{sec:samples}

\begin{center}
\begin{figure}[h]
\begin{minipage}[t]{0.5\textwidth}
\hspace{0.6cm}
%\begin{scriptsize}
\begin{tabular}{cccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (5,2) & (4,3) & (1,6) \\ 
        1 & (4,2)  & (6,5) & (3,1) \\
        2 & (6,4) & (2,1) & (3,5) \\
        3 & (6,2) & (5,0) & (1,7) \\
        4 & (5,1) & (0,6) & (2,7) \\
        5 & (7,5) & (2,0) & (6,3) \\
        6 & (0,7) & (4,1) & (3,2) \\
       7 & (7,4)  & (0,3) &  \\
       8 & (4,0)  & (7,3) &  \\
       9 & (5,4)  & (7,6) & (1,0) \\ \bottomrule
          & & & \\
          & & & \\
    \end{tabular}
%\end{scriptsize}
\label{08-06a}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
\hspace{0.6cm}
%\begin{scriptsize}
\begin{tabular}{cccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (2,7) & (3,0) & (5,4) \\ 
        1 & (0,2)  & (4,3) & (7,5) \\
        2 & (0,4) & (7,6) & (5,3) \\
        3 & (4,6) & (5,0) & (3,1) \\
        4 & (6,5) & (3,2) & (1,4) \\
        5 & (6,3) & (4,7) & (2,1) \\
        6 & (7,3) & (1,6) & (4,2) \\
       7 & (7,1)  & (2,5) & (6,0) \\
       8 & (5,1)  & (0,7) & (6,2) \\
       9 & (1,0)  & & \\ \bottomrule
          & & & \\
          & & & \\
    \end{tabular}
%\end{scriptsize}
\label{08-06b}
\end{minipage}
\caption{Schedules for 8 skippers and 6 boats. On the left is the published ISAF schedule, and this is illegal. On the right is our schedule, respecting all ISAF criteria..}
\label{08-06}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
\begin{minipage}[t]{0.3\textwidth}
\hspace{0.2cm}
\begin{scriptsize}
\begin{tabular}{cccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (0,7) & (3,2) & (5,4) \\ 
        1 & (0,2) & (7,4) & (5,3) \\
        2 & (4,0) & (7,3) & (2,5) \\
        3 & (3,0) & (2,4) & (6,5) \\
        4 & (4,3) & (5,1) & (8,6) \\
        5 & (3,1) & (6,2) & (4,8) \\
        6 & (6,3) & (1,4) & (8,2) \\
        7 & (4,6) & (2,7) & (1,8) \\
        8 & (7,6) & (0,8) & (2,1) \\
        9 & (8,7) & (5,0) & (6,1) \\
        10 & (8,5) & (1,7) & (0,6) \\
        11 & (7,5) & (3,8) & (1,0) \\ \bottomrule
    \end{tabular}
\end{scriptsize}
\label{tab3a}
\end{minipage}
%\hfill
\begin{minipage}[t]{0.3\textwidth}
\begin{scriptsize}
\begin{tabular}{ccccc}
        \toprule
        Flight & \multicolumn{4}{c}{Matches} \\ \midrule
        0 & (0,6) & (3,2) & (5,4) & (1,7) \\
        1 & (2,0) & (6,3) & (4,1) & (8,7) \\
        2 & (6,4) & (0,5) & (7,2) & (3,8) \\
        3 & (4,7) & (1,8) & (0,3) & (5,2) \\
        4 & (3,1) & (7,5) & (8,0) & (2,6) \\
        5 & (3,7) & (4,8) & (2,1) & (6,5) \\
        6 & (8,2) & (1,6) & (5,3) & (0,4) \\
        7 & (5,1) & (7,0) & (6,8) & (4,3) \\
        8 & (8,5) & (2,4) & (7,6) & (1,0) \\ \bottomrule
        & & & & \\
        & & & & \\
        & & & & \\
    \end{tabular} 
\end{scriptsize}
\end{minipage}
\caption{Three schedules. First is 8 skippers with 6 boats (legal), then 9 skippers with 6 boats (new), finally 9 skippers with 8 boats (new).}
\label{sr10}
\end{figure}
\end{center}

>>>>

\section{Sample Schedules}\label{sec:samples}
We present three pairs of schedules. The first pair is for 8 skippers and 6 boats, one published by ISAF, the other generated by us. Next, we present two new schedules, not appearing in the ISAF manual, for 9 skippers and 6 boats and 9 skippers with 8 boats. The last pair is for 10 skippers and 6 boats, again ISAF published and generated by us. For each of our schedules, we used 1 day cpu time for the first stage (minimising boat changes) then a further 2 days to minimise imbalance. Stages 3 and 4 (renaming and orientation) completed in less than a second.

\begin{center}
\begin{figure}[h]
\begin{minipage}[t]{0.5\textwidth}
\hspace{0.6cm}
%\begin{scriptsize}
\begin{tabular}{cccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (5,2) & (4,3) & (1,6) \\ 
        1 & (4,2)  & (6,5) & (3,1) \\
        2 & (6,4) & (2,1) & (3,5) \\
        3 & (6,2) & (5,0) & (1,7) \\
        4 & (5,1) & (0,6) & (2,7) \\
        5 & (7,5) & (2,0) & (6,3) \\
        6 & (0,7) & (4,1) & (3,2) \\
       7 & (7,4)  & (0,3) &  \\
       8 & (4,0)  & (7,3) &  \\
       9 & (5,4)  & (7,6) & (1,0) \\ \bottomrule
    \end{tabular}
%\end{scriptsize}
\label{08-06a}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
\hspace{0.6cm}
%\begin{scriptsize}
\begin{tabular}{cccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (2,7) & (3,0) & (5,4) \\ 
        1 & (0,2)  & (4,3) & (7,5) \\
        2 & (0,4) & (7,6) & (5,3) \\
        3 & (4,6) & (5,0) & (3,1) \\
        4 & (6,5) & (3,2) & (1,4) \\
        5 & (6,3) & (4,7) & (2,1) \\
        6 & (7,3) & (1,6) & (4,2) \\
       7 & (7,1)  & (2,5) & (6,0) \\
       8 & (5,1)  & (0,7) & (6,2) \\
       9 & (1,0)  & & \\ \bottomrule
    \end{tabular}
%\end{scriptsize}
\label{08-06b}
\end{minipage}
\caption{Schedules for 8 skippers and 6 boats. On the left, the published ISAF schedule (illegal) and on the right is our schedule.}
\label{08-06}
\end{figure}
\end{center}

\noindent
\subsection{8 skippers and 6 boats}
We first analyse the ISAF schedule (on the left). Criteria 4 (skippers in last match in a flight cannot be first in next flight) is violated on 3 occasions (skipper 1 in flight 3, skipper 7 in flight 4, skipper 0 in flight 7). Criteria 5 (no more than two consecutive port or starboard assignments) are violated for skippers 6 and 7. Criteria 6 (imbalance) is violated for skippers 6 and 8. Criteria 12  (new boats do not sail first) is violated in flight 9 for skipper 5. Finally, the schedule has 8 boat changes. Our schedule, on the right, resepects all criteria and has 6 boat changes and a maximum imbalance of 1.

\begin{center}
\begin{figure}[h]
\begin{minipage}[t]{0.5\textwidth}
\hspace{0.6cm}
%\begin{scriptsize}
\begin{tabular}{cccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (0,7) & (3,2) & (5,4) \\ 
        1 & (0,2) & (7,4) & (5,3) \\
        2 & (4,0) & (7,3) & (2,5) \\
        3 & (3,0) & (2,4) & (6,5) \\
        4 & (4,3) & (5,1) & (8,6) \\
        5 & (3,1) & (6,2) & (4,8) \\
        6 & (6,3) & (1,4) & (8,2) \\
        7 & (4,6) & (2,7) & (1,8) \\
        8 & (7,6) & (0,8) & (2,1) \\
        9 & (8,7) & (5,0) & (6,1) \\
        10 & (8,5) & (1,7) & (0,6) \\
        11 & (7,5) & (3,8) & (1,0) \\ \bottomrule
    \end{tabular}
%\end{scriptsize}
\label{09-06}
\end{minipage}
%\hfill
\begin{minipage}[t]{0.5\textwidth}
\hspace{0.6cm}
%\begin{scriptsize}
\begin{tabular}{ccccc}
        \toprule
        Flight & \multicolumn{4}{c}{Matches} \\ \midrule
        0 & (0,6) & (3,2) & (5,4) & (1,7) \\
        1 & (2,0) & (6,3) & (4,1) & (8,7) \\
        2 & (6,4) & (0,5) & (7,2) & (3,8) \\
        3 & (4,7) & (1,8) & (0,3) & (5,2) \\
        4 & (3,1) & (7,5) & (8,0) & (2,6) \\
        5 & (3,7) & (4,8) & (2,1) & (6,5) \\
        6 & (8,2) & (1,6) & (5,3) & (0,4) \\
        7 & (5,1) & (7,0) & (6,8) & (4,3) \\
        8 & (8,5) & (2,4) & (7,6) & (1,0) \\ \bottomrule
        & & & & \\
        & & & & \\
        & & & & \\
    \end{tabular} 
%\end{scriptsize}
\label{09-08}
\end{minipage}
\caption{Two new schedules. On the left, 9 skippers and 6 boats and on the right 9 skippers and 8 boats.}
\label{09}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
\begin{minipage}[t]{0.5\textwidth}
\hspace{0.6cm}
%\begin{scriptsize}
\begin{tabular}{cccc}
 \toprule
Flight & \multicolumn{3}{c}{Matches} \\ \midrule
0 & (8,3) &  (1,7) &  (0,9) \\
1 & (7,3) &  (0,8) &  (1,9) \\
2 & (0,7) &  (9,3) &  (1,8) \\ 
3 & (6,2) &  (5,0) &  (7,4) \\
4 & (5,2) &  (6,4) &  (3,0) \\ 
5 & (8,6) &  (2,9) &  (4,1) \\ 
6 & (7,2) &  (4,8) &  (9,6) \\
7 & (2,4) &  (0,6) &  (7,5) \\ 
8 & (6,1) &  (5,9) &  (8,2) \\ 
9 & (9,4) &  (8,7) &  (6,5) \\ 
10 & (9,7) &  (6,3) &  (8,5) \\ 
11 & (7,6) &  (3,1) &  (9,8) \\
12 & (4,3) &  (5,1) &  (2,0) \\ 
13 & (3,5) &  (4,0) &  (2,1) \\ 
14 & (5,4) &  (3,2) &  (1,0) \\ \bottomrule
\end{tabular}
%\end{scriptsize}
\label{10-06a}
\end{minipage}
%\hfill
\begin{minipage}[t]{0.5\textwidth}
\hspace{0.6cm}
%\begin{scriptsize}
\begin{tabular}{ccccc}
\toprule
Flight & \multicolumn{3}{c}{Matches} \\ \midrule
0 & (4,7) & (3,2) & (0,5) \\
1 & (2,4) & (7,0) & (3,5) \\
2 & (0,4) & (7,3) & (5,2) \\ 
3 & (4,3) & (0,2) & (5,7) \\ 
4 & (3,0) & (6,5) & (2,7) \\ 
5 & (6,3) & (7,1) & (8,2) \\
6 & (7,6) & (2,1) & (9,8) \\ 
7 & (2,6) & (8,7) & (4,9) \\ 
8 & (6,8) & (1,4) & (7,9) \\
9 & (8,1) & (5,4) & (9,6) \\ 
10 & (5,1) & (9,2) & (4,6) \\ 
11 & (1,9) & (6,0) & (8,4) \\ 
12 & (0,9) & (3,8) & (6,1) \\ 
13 & (8,0) & (9,5) & (1,3) \\ 
14 & (5,8) & (9,3) & (1,0) \\ \bottomrule 
\end{tabular} 
%\end{scriptsize}
\label{10-06b}
\end{minipage}
\caption{Schedules for 10 skippers and 6 boats. On the left, the ISAF published schedule (illegal) and on the right, our schedule.}
\label{10-06}
\end{figure}
\end{center}
